---
title: "R Notebook"
output: html_notebook
---
```{r}
remotes::install_github("rstudio-education/dsbox")
library(tidyverse)
library(dsbox)
```
## What are the three most common first names of purchasers?

  - ### They are Jackson, Jacob, and Joseph
```{r}
lego_sales %>%
  count(first_name)%>%
  arrange(desc(n))
```
## What are the three most common themes of Lego sets purchased?

  - ### They are Star Wars, Nexo Knights, and Gear
```{r}
lego_sales %>%
  count(theme)%>%
  arrange(desc(n))
```
## Among the most common theme of Lego sets purchased, what is the most common subtheme?

  - ### They are NA, Ultimate, and The Force Awakens
```{r}
lego_sales %>%
  filter(theme=="Star Wars"|theme=="Nexo Knights"|theme=="Gear")%>%
  count(subtheme) %>%
  arrange(desc(n))
```
## Create a new variable called age_group and group the ages into the following categories: “18 and under”, “19 - 25”, “26 - 35”, “36 - 50”, “51 and over”.

  - ### please see the table below
```{r}
lego_sales$age_group <- lego_sales$age 
lego_sales$age_group <- case_when(
  lego_sales$age_group <= 18 ~ "18 and under",
  lego_sales$age_group >=19&lego_sales$age_group<=25 ~ "19 - 25",
  lego_sales$age_group >=26&lego_sales$age_group<=35 ~ "26 - 35",
  lego_sales$age_group >=36&lego_sales$age_group<=50 ~ "36 - 50",
  lego_sales$age_group >= 51 ~ "51 and over",
)
lego_sales
```
## Which age group has purchased the highest number of Lego sets.

  - ### The 36-50 group has purchased the highest number of Lego sets
```{r}
lego_sales %>%
  group_by(age_group) %>%
  summarize(Count=n()) %>%
  arrange(desc(Count))
```

## Which age group has spent the most money on Legos?

  - ### The 36-50 group has spent the most money on Legos
```{r}
lego_sales$money <- lego_sales$quantity * lego_sales$us_price
arrange(summarise(group_by(lego_sales,age_group),money_spend=sum(quantity*us_price)),desc(money_spend))
```
## Which Lego theme has made the most money for Lego?

  - ### The Star Wars has made the most money for Lego
```{r}
arrange(summarise(group_by(lego_sales,theme),theme_money_spend=sum(quantity*us_price)),desc(theme_money_spend))
```

## Which area code has spent the most money on Legos? In the US the area code is the first 3 digits of a phone number.

  - ### If NA does not count, then area code "956" has spent the most money on Legos
```{r}
lego_sales$area_code <- str_sub(lego_sales$phone_number, 1, 3)
lego_sales %>%
  group_by(area_code) %>%
  summarise(area_code_money_spend=sum(quantity*us_price)) %>%
  arrange(desc(area_code_money_spend))
```
## What are the top 5 name that contributed the most sales for Lego

  - ### From the graph below we can see the difference between the top 5 Lego name sold 

```{r}
name <- lego_sales %>%
  group_by(name) %>%
  summarise(name_money_spend=sum(quantity*us_price)) %>%
  arrange(desc(name_money_spend))
name <-  top_n(name,5)
ggplot(data = name, aes(x = name_money_spend, y = name)) +
  geom_point()
```